The Ranked Nearest Neighbour Interchange space

### 2019-05-26 paper.tex
change formulation lemma:caterpillar_dist=diameter

\begin{lemma}
    Let $T$ and $T'$ be two caterpillar trees with distance $d(T,T') = \Delta(\rnniu) = \frac{(n-1)(n-2)}{2}$.
    There is a shortest path between $T$ and $T'$ that is a caterpillar path.
    \label{lemma:caterpillar_dist=diameter}
\end{lemma}

@@

    Let $T$ and $T'$ have distance $d(T,T') = \Delta(\rnniu)$.
    We can compute a  shortest caterpillar path from $T$ to $T'$ using Bubble Sort.
    In each loop $k=1, \ldots, n-2$ of the algorithm there can be at most $n-2-k$ exchanges of taxa.
    It follows that the maximum length of a path computed by Bubble Sort is $\sum\limits_{k=1}^{n-2} k = \frac{(n-1)(n-2)}{2}$.
    Since there cannot be a caterpillar path shorter than $\frac{(n-1)(n-2)}{2}$, if the distance is $d(T,T') \frac{(n-1)(n-2)}{2}$, it follows $d_c(T,T') = \Delta(\rnniu)$.

>>>>

\begin{lemma}
    Let $T$ and $T'$ be two caterpillar trees.
    $T$ and $T'$ have distance $d(T,T') = \Delta(\rnniu) = \frac{(n-1)(n-2)}{2}$ if, and only if, they have caterpillar distance $d_c(T,T') = \Delta(\rnniu) = \frac{(n-1)(n-2)}{2}$. \todo{define $d_c$}
    \label{lemma:caterpillar_dist=diameter}
\end{lemma}

@@

    Let $T$ and $T'$ have distance $d(T,T') = \Delta(\rnniu)$.
    We can compute a  shortest caterpillar path from $T$ to $T'$ using Bubble Sort.
    In each loop $k=1, \ldots, n-2$ of the algorithm there can be at most $n-2-k$ exchanges of taxa.
    It follows that the maximum length of a path computed by Bubble Sort is $\sum\limits_{k=1}^{n-2} k = \frac{(n-1)(n-2)}{2}$.
    Since there cannot be a caterpillar path shorter than $\frac{(n-1)(n-2)}{2}$ if it is $d(T,T') = \frac{(n-1)(n-2)}{2}$, it follows $d_c(T,T') = \Delta(\rnniu)$.
